The \dealii{} Library, Version 9.2

### 2020-06-04 9.2/paper.tex
Resolve one TODO.

  \item xy \todo[inline]{Update once we have the subsections in Section 2;
          provide cross-references to each of these subsections}
        %   \item Improved support for automatic differentiation (see
        %     Section~\ref{subsec:ad}),

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances of the SIMD capabilities and the matrix-free infrastructure}
\label{subsec:mf}

>>>>

  \item A new, parallel, fully distributed triangulation class (see
        Section~\ref{subsec:pft});
  \item Substantially improved performance for very large computations
    on tens or hundreds of thousands of processor cores and up to
    trillions of unknowns (see
        Section~\ref{subsec:performance});
  \item Better support for parallel $hp$-adaptive algorithms (see
        Section~\ref{subsec:hp});
  \item Support for particle-based methods (see
        Section~\ref{subsec:particles});
  \item Improved performance of the symbolic differentiation framework (see
        Section~\ref{subsec:symbdiff});
  \item Advances in SIMD capabilities and the matrix-free infrastructure (see
        Section~\ref{subsec:mf});
  \item Advances in GPU support (see
        Section~\ref{subsec:gpu});
  \item Better use of modern C++ language features (see
        Section~\ref{subsec:cxx});
  \item Seven new tutorial programs (see
        Section~\ref{subsec:steps}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advances in SIMD capabilities and the matrix-free infrastructure}
\label{subsec:mf}
